Title

### 2013-03-20 inc/hardware/column.tex
clean up the introductions to the hardware and consideration sections

Apart from the laser system, the majority of an Ultrafast Electron Microscope column is either vacuum hardware or contained within the vacuum system.
It is common in the UEM field to modify an existing Transmission Electron Microscope column, adapting it for laser-stimulated electron generation.
The system presented in the following section has been designed and built either from scatch or from commercially available parts.
The reasons for this are two-fold, the ease of prototyping inherent in using replacable parts and the physical limitations our unique choices have imposed on our beam profile.

@@

The vacuum chamber itself is almost entirely 4.5 in standard ConFlat hardware.
Much has been purchased from off-the-shelf hardware suppliers.
More complicated chamber components have been fabricated in-house or purchased from Kimball Physics Inc.

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube,'' having six 4.5 in ConFlat ports on a cube, with eight 1.33 in ports on the corners.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''
This system is used to mount the accelerator anode and the the deflector plates which are both to be described later.

>>>>

Apart from the laser system, the majority of an Ultrafast Electron Microscope column is either vacuum hardware or contained within the vacuum system.
The vacuum chamber itself is almost entirely 4.5 in standard ConFlat hardware.
Much has been purchased from off-the-shelf hardware suppliers.
Some of the more specialized chamber components have been fabricated in-house or purchased from Kimball Physics Inc.

@@

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube,'' a large stainless-steel sphere which has six 4.5 in ConFlat ports oriented as a cube, with another eight 1.33 in ports on the corners of the cube.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''
This system is used to mount the accelerator anode and the the deflector plates which are both to be described later.

### 2013-03-20 inc/hardware/introduction.tex
clean up the introductions to the hardware and consideration sections

>>>>

It is common in the DTEM field to modify an existing Transmission Electron Microscope column, adapting it for laser-stimulated electron generation.
For the reasons covered in Section \ref{sec:childs_law}, the prototype UEM at UIC is being built to accomodate large width electron pulses.
To satisfy this restriction, it has been designed and built from parts either fabricated in-house or from commercially available, both for the ease of prototyping inherent in using replacable parts and the accomodate the physical limitations our choice of a large beam width have imposed on the standard electron microscope column components.

In this chapter, I will first describe the laser system which was custom built for the prototype UEM system being constructed at UIC.
I will then describe how we have addressed the necessity of the large-area electron beam in each of the individual components of the UEM column.
